|

### 2021-03-21 documentation/paper.Rmd
Thank Hannah Willis

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback. We would also like to thank X, Y, and Z for offering their time to review the manuscript. Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.1) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}

>>>>

---
title: |
  | PollBasePro: Daily Estimates of Aggregate Voting Intention in Britain from `r format(min(britpol::pollbasepro$date), "%Y")` to the Present Day\thanks{This article benefitted from much useful feedback. We owe particular thanks to Chris Hanretty, who inspired this project and provided much useful feedback. We would also like to thank Hannah Willis, Y, and Z for offering their time to review our manuscript. Finally, we would like to extend a special thanks to all of the volunteers who work to maintain such a comprehensive list of British opinion polling data on Wikipedia.}
author: |
  | Jack Bailey\thanks{Research Associate, Department of Politics, University of Manchester, UK. If you have any comments or questions, feel free to contact me either by email (\href{mailto:jack.bailey@manchester.ac.uk}{jack.bailey@manchester.ac.uk}) or on Twitter (\href{https://www.twitter.com/PoliSciJack}{@PoliSciJack}).}, Mark Pack\thanks{President, The Liberal Democrats, UK}, & Luke Mansillo\thanks{PhD Candidate, Department of Government \& International Relations, University of Sydney, Australia}
date: |
  | \small This version compiled `r stringr::str_remove(format(Sys.time(), '%d %B %Y'), "^0")` using PollBasePro `r paste0("v", packageVersion("britpol"))`
abstract: |
  | Political scientists often use public opinion polls to test their theories. Yet these data present some difficulties. First, they are noisy. Second, they occur at irregular intervals. Third, they measure both public preferences and pollsters' survey design choices. We introduce a new dataset, PollBasePro, that accounts for these issues. It includes voting intention estimates for each of Britain's three largest parties on each day between the 1955 general election and the present. Given that the dataset covers `r format(nrow(britpol::pollbasepro), big.mark = ",")` days in total, it is more comprehensive than any existing time series of public opinion in Britain. As a result, we expect PollBasePro to be an important resource for students of British politics in the years to come.
  |
  | \textbf{\textsf{Keywords:}} Opinion polls; public opinion; British politics; Bayesian methods.
indent: yes
fontsize: 12pt
geometry: margin = 1.15in
subparagraph: yes
compact-title: false
bibliography: _assets/master.bib
biblio-style: _assets/apsr.bst
classoption: a4paper
linkcolor: black
urlcolor: violet
citecolor: black
output: 
  bookdown::pdf_document2: 
    latex_engine: xelatex
    toc: false
    keep_tex: false
    includes:
      in_header:
        - _assets/rmd-preamble.tex
    number_sections: false
    fig_caption: true
---

@@

\begin{align*}
Poll_{i} &\sim \mathrm{Normal}(\mu_{i}, \sqrt{\sigma^2 + S_{i}^2}) \srlab{Likelihood function} \\
\mu_{i} &= \alpha_{Day[i]} + \delta_{Pollster[i]} \srlab{Measurement model on $\mu$} \\
\alpha_{t} &= \alpha_{t-1} + \tau \omega_{t-1} \text{ for } t \text{ in } 2, ..., T-1 \srlab{Dynamic model on $\alpha_{t}$} \\
\alpha_{T} &\sim \mathrm{Normal}(\alpha_{T-1}, \tau) \srlab{Adaptive prior on $\alpha_{T}$} \\
\delta_{j} &\sim \mathrm{Normal}(0, 0.05) \text{ for } j \text{ in } 1, ..., J \srlab{Prior on house effects, $\delta$} \\
\omega_{t} &\sim \mathrm{Normal}(0, 0.025) \text{ for } t \text{ in } 1, ..., T-1 \srlab{Prior on random shocks, $\omega$} \\
\tau &\sim \mathrm{Normal}(0, 0.05)^{+} \srlab{Positive prior on scale of innovations, $\tau$} \\
\sigma &\sim \mathrm{Exponential}(20) \srlab{Prior on residual error, $\sigma$} \\
\end{align*}
